\documentclass[letterpaper,10pt]{article}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
\usepackage[default]{sourcesanspro}

% Colors
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

% Custom Commands
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

\renewcommand\labelitemi{--}

\begin{document}

% Heading
\documentTitle{\href{https://1md3nd.com}{Anurag Ranjan}}{
  \href{mailto:anurag.ranjan@impressico.com}{\raisebox{-0.15\height}\faEnvelope\ anurag.ranjan@impressico.com} ~ | ~
  \href{https://linkedin.com/in/1md3nd}{\raisebox{-0.15\height}\faLinkedin\ linkedin.com/in/1md3nd} ~ | ~
  \href{https://github.com/1md3nd}{\raisebox{-0.15\height}\faGithub\ github.com/1md3nd}
}

% Education (Position 1)
\section{Education}

\headingBf{KIET Group of Institutions}{2019 -- 2023}
\headingIt{Bachelor of Technology in Information Technology}{CGPA: 8.14}

% Work (Position 2)
\section{Work}

\headingBf{ \href{https://www.impressico.com}{Impressico Business Solutions}}{Jan 2024 -- Present}  
\headingIt{DevOps Trainee Engineer}{}
\begin{resume_list}  
  \item \textbf{Tech Stack:} AWS, Terraform, CloudFormation, Jenkins, Docker, Kubernetes, Prometheus, Grafana
  \item Engineered \textbf{\color{accentTitle}{CI/CD pipelines}} to streamline deployments and accelerate releases.
  \item Automated \textbf{\color{accentTitle}{infrastructure provisioning}} with Terraform \& CloudFormation, reducing manual intervention.
  \item Deployed \textbf{\color{accentTitle}{monitoring solutions}} with Prometheus and Grafana for high availability.
  \item Collaborated with teams to quickly \textbf{\color{accentTitle}{diagnose and resolve}} deployment issues.
  \item Conducted RCA to implement \textbf{\color{accentTitle}{proactive measures}} and boost system stability.
\end{resume_list}

\headingBf{\href{https://www.healthcart.com}{HealthKart}}{Jan 2023 -- July 2023} 
\headingIt{Software Development Engineer Intern \href{https://drive.google.com/file/d/1Iz83NKtrG7A1KG_rK0P8s_sAquzRm_OY/view?usp=sharing}{\small\textit{\color{gray}{Link}}}}{}
\begin{resume_list}
  \item \textbf{Tech Stack:} Node.js, Express, RESTful APIs, Postman
  \item Developed and rigorously tested \textbf{\color{accentTitle}{RESTful APIs}} to improve backend performance.
  \item Collaborated in agile teams to \textbf{\color{accentTitle}{debug and resolve}} critical issues.
  \item Participated in code reviews to uphold coding standards.
\end{resume_list}

% Skills (Position 3)
\section{Skills}
\begin{multicols}{2}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=75pt]
    \item[\textbf{Programming}] Python, Shell Scripting, Node.js
    \item[\textbf{Cloud}] AWS, CloudFormation
    \item[\textbf{DevOps}] Jenkins, Prometheus, Grafana
    \item[\textbf{Containers}] Docker, Kubernetes
    \item[\textbf{Databases}] MySQL, MongoDB, Elasticsearch
    \item[\textbf{Tools}] Terraform, Ansible
  \end{itemize}
\end{multicols}

% Projects (Position 4)
\section{Projects}

\headingBf{Kubernetes The Hard Way \href{https://github.com/1md3nd/k8s}{\small\textit{\color{gray}{Link}}}}{}
\begin{resume_list}
  \item \textbf{Tech Stack:} Kubernetes, Shell scripting, Terraform 
  \item Architected and deployed Kubernetes clusters from scratch, adhering to industry best practices.
  \item Gained advanced expertise in \textbf{\color{accentTitle}{cluster management, scaling, and security configurations}}.
\end{resume_list}

\headingBf{Serverless Full-Stack Portfolio with Automated DevOps Lifecycle \href{https://github.com/1md3nd/portfolio}{\small\textit{\color{gray}{Link}}}}{}
\begin{resume_list}
  \item \textbf{Tech Stack:} AWS (S3, CloudFront, Lambda, API Gateway, DynamoDB), React.js, GitHub Actions, CloudFormation 
  \item Architected and deployed a dynamic, serverless portfolio website ensuring high scalability and \textbf{\color{accentTitle}{99.99\% uptime}}.
  \item Developed a CI/CD pipeline with GitHub Actions and CloudFormation, reducing deployment time by \textbf{\color{accentTitle}{50\%}}.
  \item Built a responsive React.js front-end to enhance user engagement and performance.
  \item Optimized infrastructure costs and performance using AWS best practices.
\end{resume_list}

% Achievements (Position 5)
\section{Achievements}
\headingBf{KIET Codechef Chapter Executive Member}{}
\begin{resume_list}
  \item Organized and managed coding events, boosting competitive programming participation.
\end{resume_list}

\headingBf{Leetcode Success \href{https://www.leetcode.com/1md3nd}{\small\textit{\color{gray}{Link}}}}{}
\begin{resume_list}
  \item \textbf{\color{accentTitle}{Solved over 600 algorithm problems}}, demonstrating strong problem solving skills and dedication.
\end{resume_list}

\headingBf{Postman API Student Expert}{}
\begin{resume_list}
  \item Recognized for excellence in \textbf{\color{accentTitle}{API design, testing, and automation}} using Postman.
\end{resume_list}

% Certifications (Bottom)
\section{Certifications}
\begin{resume_list}  
  \item \headingBf{\href{https://www.coursera.org/account/accomplishments/verify/VAXY9EEWXD3C}{Introduction to Git and GitHub}}{}
  \item \headingBf{\href{https://www.coursera.org/account/accomplishments/verify/MEHYBBVAYE8E}{Data Structures and Performance}}{}
  \item \headingBf{\href{https://www.coursera.org/account/accomplishments/verify/R73VUS4L44RN}{Palo Alto Networks Academy Cybersecurity Foundation}}{}
  \item \headingBf{\href{https://drive.google.com/file/d/15n4G1_3d75gbxfikhzodotRZVXInxqhJ/view?usp=sharing}{CCNAv7: Introduction to Networks}}{}
\end{resume_list}

\end{document}
