\documentclass[letterpaper,10pt]{article}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
\usepackage[default]{sourcesanspro}

% Colors
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

% Custom Commands
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

\renewcommand\labelitemi{--}

\begin{document}

% Heading
\documentTitle{\href{https://rakeshinfo.xyz}{Rakesh Singh}}{
  \href{mailto:singh.rakesh04107@gmail.com}{\raisebox{-0.15\height} 
  \faEnvelope\ singh.rakesh04107@gmail.com} ~ | ~
  \href{https://www.linkedin.com/in/rakesh-singh-0113a1186}{\raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/rakesh-singh-0113a1186} ~ | ~
  \href{https://github.com/Rakesh04107}{\raisebox{-0.15\height} \faGithub\ github.com/Rakesh04107} ~ | ~
  Bengaluru
}
% Summary
\tinysection{Summary}
DevOps enthusiast with hands-on experience in cloud technologies, infrastructure as code, and CI/CD pipelines. Experienced in Python, Shell Scripting, AWS, Docker, Kubernetes, and more. Proven ability to solve complex problems, manage projects and deliver results.

% Skills
\section{Skills}
\begin{multicols}{2}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=75pt]
    \item[\textbf{ Scripting}] Python, Shell Scripting, Node.js
    \item[\textbf{Cloud Platforms}] AWS-EC2, S3, Lambda, RDS, IAM, VPC, CloudFront, CloudFormation, cloud watch,Route 53,
    \item[\textbf{DevOps}] Docker, Kubernetes, Git, Jenkins, Terraform, GitHub Actions
    \item[\textbf{Containers}] Docker, Kubernetes
    \item[\textbf{CI/CD}] GitHub Actions, Jenkins pipelines
    \item[\textbf{Infrastructure}] Windows Server, Linux Administrator, Active Directory, DNS, INTUNE, DHCP
  \end{itemize}
\end{multicols}

% Experience
\section{Experience}

\headingBf{\href {https://www.impressico.com}{ WIPRO TECHNOLOGIES PAYROLL {RENOVISION}}{Nov 2021 -- Present} } 
\headingIt{SYSTEM ADMINISTRATOR}{}  
\begin{resume_list}  
  \item Automated routine server management tasks using PowerShell and Terraform.  
  \item  Supported internal cloud migration projects by provisioning AWS services (EC2, IAM, S3, VPC) for dev/test
 environments.
  \item Deployed and monitored AWS EC2 instances and managed hybrid infrastructure using Active Directory and
 VMware.
  \item Implemented basic CI pipelines for internal applications using Jenkins and GitHub Actions.
  \item Monitored AWS and on-premises workloads using AWS CloudWatch and Secure RT.
\end{resume_list}


\headingBf{\href{https://www.healthcart.com}{HealthKart}}{Jan 2023 -- July 2023} 
\headingIt{\href {https://drive.google.com/file/d/1Iz83NKtrG7A1KG_rK0P8s_sAquzRm_OY/view?usp=sharing}{Software Development Engineer Intern}}{}
\begin{resume_list}
  \item Supported the development and testing of RESTful APIs, improving back-end functionality.
  \item Collaborated with team members during debugging and troubleshooting sessions to improve system reliability.  
  \item Participated in code reviews and team meetings to understand project workflows and improve coding standards.  
\end{resume_list}


% Education
\section{Education}

\headingBf{KIET Group of Institutions}{2019 -- 2023}
\headingIt{Bachelor of Technology in Information Technology}{CGPA: 8.14}

% Certifications
\section{Certifications}
\begin{resume_list}  

\item \headingBf{\href {AWS CERTIFIED CLOUD PRACTITIONER  - 2024}}{}

\item \headingBf{\href { AWS CERTIFIED SOLUTION ARCHITECT - ASSOCIATE - 2025}}{}

\item \headingBf{\href { DevOps Beginners to Advanced ( Hands-on Projects) - 2025}}{}

\item \headingBf{\href {CYBER SECURITY AWARENESS - 2024}}{}
\end{resume_list}

% Projects
\section{Projects}

\headingBf{ Vprofile App - Cloud Hosted Profile Portal}{}
\begin{resume_list}
  \item •Configured S3 for object storage and EFS for shared storage.
  \item •Deployed infrastructure with AWS EC2 instances behind Elastic Load Balancer and Auto Scaling groups.
  \item •Set up Route 53 for DNS management and high availability.
  \item  •Impact: Achieved 99.9prnt uptime, improved scalability, and reduced infrastructure costs by 20prnt.
\end{resume_list}

\headingBf{\href {EMart – Cloud-Native E-commerce App Deployment (Full DevOps Pipeline)}}{}
\begin{resume_list}
  \item  • Containerized all services and managed deployment with Kubernetes.
  \item  • Configured Nginx as an API gateway.
  \item  • Used Jenkins and GitHub Actions to automate build and deployment.
  \item  • Reduced manual deployment efforts by 80 % and improved reliability.

\end{resume_list}

% Achievements
\section{Achievements}
\headingBf{KIET Codechef Chapter Executive Member}{}
\begin{resume_list}
\item Organized and managed coding events, promoting competitive programming and student engagement.
\end{resume_list}

\headingBf{\href {https://www.leetcode.com/1md3nd}{Leetcode} and Codechef Success}{}
\begin{resume_list}
\item Solved more than 600 problems on Leetcode, demonstrating strong problem solving and algorithm skills.
\end{resume_list}

\headingBf{Postman API Student Expert}{}
\begin{resume_list}
\item Achieved distinction in API design and testing using Postman.
\end{resume_list}
\end{document}
